Supplementary Material for Asymmetry paper

### 2020-06-24 Supplementary/Sup_mat.Rmd
More updates

```{r Two_Throws_Priors_only_model, include = T, echo = F, cache = T}
Two_throw_priors <- brm(
  abspos ~ 0 + norm_delta * Num_throws + (0 + norm_delta * Num_throws|Participant),
  family = "beta",
  data = model_data_pos,
  prior = TT_prior,
  cores = 1,
  chains = 1,
  iter = TT_iter,
  warmup = TT_iter/2,
  control = TT_control,
  sample_prior = "only")
```

@@

```{r Two-throws modelling, include = T, echo = F, cache = T}

>>>>

```{r Two_Throws_Priors_only_model, include = T, echo = T, message = F, warning = F, cache = TRUE}
Two_throw_priors <- brm(
  abspos ~ 0 + norm_delta * Num_throws + (0 + norm_delta * Num_throws|Participant),
  family = "beta",
  data = model_data_pos,
  prior = TT_prior,
  cores = 1,
  chains = 1,
  iter = TT_iter,
  warmup = TT_iter/2,
  control = TT_control,
  sample_prior = "only")
```

@@

```{r Two-throws modelling, include = T, echo = T, message = F, warning = F, cache = T}
